### 2024-06-13 player-evaluation.qmd
20240613 - code folding

```{r}
set.seed(1)

@@

Other factors to consider include cognitive and motivational factors.
Some coaches refer to these as the "X Factor" or "the intangibles."
However, just as any other construct in psychology, we can devise ways to operationalize them.

@@

```{r}
exampleData <- data.frame(
  player = c(rep("A", 3), rep("B", 3)),
  expert = c(1:3, 1:3),
  projectedPoints = c(300, 310, 290, 400, 300, 200)
)

@@

playerA_mean
playerB_mean
```

@@

```{r}
playerA_sd <- sd(exampleData$projectedPoints[which(exampleData$player == "A")])
playerb_sd <- sd(exampleData$projectedPoints[which(exampleData$player == "B")])

playerA_cv <- playerA_mean / playerA_sd
playerB_cv <- playerB_mean / playerb_sd

playerA_sd
playerb_sd

>>>>

```{r}
#| code-fold: true

set.seed(1)

@@

Other factors to consider include cognitive and motivational factors.
Some coaches refer to these as the "X Factor" or "the intangibles."
However, just as any other construct in psychology, we can devise ways to operationalize them.
Insofar as they are observable, they are measurable.

@@

```{r}
#| code-fold: true

exampleData <- data.frame(
  player = c(rep("A", 3), rep("B", 3)),
  expert = c(1:3, 1:3),
  projectedPoints = c(300, 310, 290, 400, 300, 200)
)

@@

playerA_sd <- sd(exampleData$projectedPoints[which(exampleData$player == "A")])
playerB_sd <- sd(exampleData$projectedPoints[which(exampleData$player == "B")])

playerA_cv <- playerA_mean / playerA_sd
playerB_cv <- playerB_mean / playerb_sd
```

```{r}
playerA_mean
playerB_mean
```

@@

```{r}
playerA_sd
playerB_sd
